---
title: "FLIC - Preference Index calculations (Towards Well A)"
author: "JP"
date: "November 10, 2016"
output: html_document
---
## Preference index calculations using myFLIC functions

```{r setup, include=FALSE, echo=F}
#Clean the environmenta and load the functions. 
library(knitr)
library(dplyr)
knitr::opts_chunk$set(echo = F)
rm(list = ls()) 
# Change this directory to where myFLIC.R file is located
#setwd("/Users/jpinzon/Documents/UTSW/Projects/01 Jmjc Project/03 Feeding preference/00 FLIC/")
source("/Users/jpinzon/Documents/UTSW/Projects/01 Jmjc Project/03 Feeding preference/00 FLIC/myFLIC.R")
```

These are general commands that refer to a particular set of functions to determine the preference index on a
determined test (i.e. path_to_file). 

There are additional options in the source file. 

```{r, echo = FALSE, results="hide"}
# Change the path accordinly to where the DFM files are. 
path_to_files="/Users/jpinzon/Documents/UTSW/Projects/01 Jmjc Project/03 Feeding preference/00 FLIC/70119m1-5"

# PI based on counts
PIs_counts=sum_PI(path_to_files,0,1,1)
PIs_counts_t=kable(PIs_counts, align='c', caption="PI based on counts")

# PI based on duration of the events
PIs_duration=sum_PI(path_to_files,0,2,1)
PIs_duration_t=kable(PIs_duration, align='c', caption="PI based on duration of the events")

# Summary of licks based on duration
resu_Licks=sum_PI(path_to_files,0,3,1)
resu_Licks_t=kable(resu_Licks, align='c', caption="Summary licks (based on dutarion)")

# Summary based on duration
resu_All=(sum_PI(path_to_files,0,3,4))
resu_All_t=kable(resu_All, align='c', caption="Summary ALL events (based on dutarion)")
```
 __These are the PI's by duration for all licks:__
`r PIs_duration_t`

 __These are the PI's by counts for all licks:__
`r PIs_counts_t`

 __Summary of counts and times for all licks:__
`r resu_Licks_t`

 __Summary of counts and times for all events:__
`r resu_All_t`